Internal models of type theory

### 2013-10-29 article-models-defn.tex
definition of weak omega groupoids
conjectured an equivalent definition of groupoids

>>>>

\subsection{Weak $\omega$-groupoids}

A weak omega groupoid is a model of type theory with $\Sigma$ and $\idtypevar{}$
in which there is a term of $\terms{A}$ for every type $A$ in context $\Gamma$.

We could also state that for every term $f:\terms{\ctxwk{A}{B}}$ and every
family $Q:\tftyp{\mfM}{\ctxext{\Gamma}{B}}$ there is a function
$\terms{\subst{f}{\ctxwk{A}{Q}}}\to\terms{Q}$ (asserting that $f$ is a trival
cofibration). This should be equivalent to the previous condition.
